Individual Differences Across Visual Search Tasks

### 2017-02-03 writeup/manuscript.tex
write up correction and note on sample size.

\subsection{Participants}
How many? Will all testing be done at the University of Aberdeen? How do we justify our sample size (a question commonly asked by journals now!)?

@@

@@

>>>>

\subsection{Participants}
We aim to find 64 participants to volunteer to take part in this experiment. Participants will be students from the University of Aberdeen, and will be compenstate £x.xx for their time. Sample size was determined in part due to constraints with counter-balancing <expand>.

@@

Following \cite{irons-leber2016}, individual differences will be characterized using two measures:\\
1) Proportion of optimal choices on plateaus. An optimal choice is defined as responding to whichever of the two target colours has the fewest items in the display. This will be based on correct plateau trials only. \\ 
2) Switching frequency. Switching is defined as responding to a different target color on trial $N$+1 than on trial $N$, and is presented as a proportion of the total number of trials (excluded incorrect trials, the trial after an incorrect trial, and the first trial of each block).\\
Both measures have been shown to correlate with overall RT in previous experiments (Proportion Optimal $r$=-.56, $p$<.001; Switch Frequency $r$=.45, $p$=.001; based on $N$=50 and using the same number of trials as in the current experiment). As additional validation, correlational analyses between both measures and RT will also be conducted in the current experiment.

@@

Data analysis will follow \cite{kristjansson2014} and Johannesson et al. (2016). The main measure of interest will be the average run length per trial. A run is defined as a succession of one or more of the same target type which is followed and preceded by the other target type or no target. The average length is the average number of consecutive target selections per run. As with the other experiments, we will also measure the average response (time to select the final target on correct trials).
